---
title: |
  | Central Valley Enhanced
  | Acoustic Tagging Project
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
```

```{r logos, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/NOAA logo.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:0px; right:0px; width:100px;')
htmltools::img(src = knitr::image_uri("../data/BureauOfReclamation.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:110px; width:200px;')
```

<br/>


## Background

There is a well documented need for improved detection and associated modeling of salmon migration and survival in the Central Valley. We propose to address this need through an expanded acoustic receiver network and associated real-time and retrospective modeling of the data. The proposed work includes (1) the deployment of real-time receivers that will provide timely information on migrating salmon smolt location and timing, (2) expansion of the existing autonomous acoustic array to increase the coverage and detection efficiency; (3) development of new metrics for the real-time data for key management relevant questions such as entrainment estimates at critical junctions (Georgiana Slough and Delta Cross Channel); and (4) a retrospective analyses directly geared toward improving the quality and robustness of an existing forecasting model -- the NMFS enhanced particle tracking model.

## Statement of Research

The San Francisco Bay-Delta is both the hub for the infrastructure for California&rsquo;s water supply and critical migratory and rearing habitat for four native runs of Chinook salmon. Understanding salmon survival and migration dynamics in the Delta and its tributaries is critical to the operation of state and federal water projects, recovery of ESA-listed species, and sport and commercial fisheries management. Tracking the fate of individual tagged fish can be accomplished with acoustic tagging (AT), tracking groups of AT fish can be used to develop estimates of survival and movement for other non-AT fish also part of that group, and population level sampling programs can use survival estimates generated by AT and applied to other mass marked (coded wire tagging; CWT) groups to develop improved capture efficiency for these sampling programs.  These capture efficiency estimates can then be used to estimate abundance of non-tagged populations. 

## Research Objectives 

This work will have significant implications for understanding movement, distribution, and survival of all four runs of Central Valley Chinook salmon. For more information on specific runs and our preliminary efforts in real-time tracking of these fish, click on a link below:

[Hatchery-origin late-fall Chinook salmon](https://calfishtrack.github.io/real-time/pageCHLF.html)

[Hatchery-origin winter-run Chinook salmon](https://calfishtrack.github.io/real-time/pageLSWR.html)

[Natural-origin spring-run Chinook salmon](https://calfishtrack.github.io/real-time/pageBCSR.html)

[Natural-origin green sturgeon](https://calfishtrack.github.io/real-time/pageSRGS.html)

<br />

## Detection Data

For downloading detection data from the receiver array, visit our Shiny app:

[CalFishTrack Shiny app](http://oceanview.pfeg.noaa.gov/shiny/FED/CalFishTrack/)

<br />

## Receiver deployments

For more information on where and when receivers are deployed, visit our receiver deployment page:

[Receiver Deployments](https://calfishtrack.github.io/real-time/pageDEPLOY.html)

<br />

## Project Reports

None currently available.

<br />

## Study Area




#### Map of receiver and release locations in the Central Valley

```{r map 1, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/JSATS_Full.png"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```

<br />

#### Closeup map of receiver locations in the Sacramento-San Joaquin Delta

```{r map 2, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/JSATS_Delta.png"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```

<br />
<br />

<br />

For realtime tracking diagnostics, click here:
[Real-time tracking diagnostics](https://calfishtrack.github.io/real-time/pageREAL.html)
