---
title: CalFishTrack

output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
```


#  *Central Valley Enhanced*
#  *Acoustic Tagging Project*
```{r logos, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')

```

<br/>


## Background

There is a well documented need for improved detection and associated modeling of salmon migration and survival in the Central Valley. We propose to address this need through an expanded acoustic receiver network and associated real-time and retrospective modeling of the data. The proposed work includes (1) the deployment of real-time receivers that will provide timely information on migrating salmon smolt location and timing, (2) expansion of the existing autonomous acoustic array to increase the coverage and detection efficiency; (3) development of new metrics for the real-time data for key management relevant questions such as entrainment estimates at critical junctions (Georgiana Slough and Delta Cross Channel); and (4) a retrospective analyses directly geared toward improving the quality and robustness of an existing forecasting model -- the NMFS enhanced particle tracking model.

## Statement of Research

The San Francisco Bay-Delta is both the hub for the infrastructure for California&rsquo;s water supply and critical migratory and rearing habitat for four native runs of Chinook salmon. Understanding salmon survival and migration dynamics in the Delta and its tributaries is critical to the operation of state and federal water projects, recovery of ESA-listed species, and sport and commercial fisheries management. Tracking the fate of individual tagged fish can be accomplished with acoustic tagging (AT), tracking groups of AT fish can be used to develop estimates of survival and movement for other non-AT fish also part of that group, and population level sampling programs can use survival estimates generated by AT and applied to other mass marked (coded wire tagging; CWT) groups to develop improved capture efficiency for these sampling programs.  These capture efficiency estimates can then be used to estimate abundance of non-tagged populations. 

## Research Objectives 

This work will have significant implications for understanding movement, distribution, and survival of all four runs of Central Valley Chinook salmon. For more information on specific runs and the real-time tracking of these fish, click on a link in the drop-down "Study Population Detections" menu.

<br />

## Telemetry Summary Forms

Every year, telemetry researchers from multiple organizations and agencies utilize the receivers deployed and data tools developed as part of this project. We request that if there is interest is utilizing these resources, please fill out this [summary form](https://github.com/CalFishTrack/real-time/blob/master/data/Telemetry_Study_Summary_Framework_BlankTemplate.docx?raw=true) prior to your study's releases, and to send the form as well as coordinate tag codes with the tag code coordinator (Arnold Ammann <arnold.ammann@noaa.gov>). Receiving this information is critical to utilizing the data visualization tools so that databases are aware of your tag codes. We request that after your study, you provide us with an updated telemetry summary form.  

## Receiver deployments

For more information on where and when receivers are deployed, visit our receiver deployment page:

[Receiver Deployments](https://calfishtrack.github.io/real-time/pageDEPLOY.html)

<br />


## Detection Data

For downloading *preliminary* real-time detection data from the receiver array, visit our ERDDAP page:

[CalFishTrack ERDDAP page](http://oceanview.pfeg.noaa.gov/erddap/tabledap/FEDcalFishTrack.subset)

<br />

For downloading *QAQCed and Final* real-time and autonomous detection data from the receiver array from 2013-2018, visit our other ERDDAP page. Note, detections from the current water year will typically be made available in October:

[Archived detections ERDDAP page](https://oceanview.pfeg.noaa.gov/erddap/tabledap/FED_JSATS.subset)

<br />

## SHINY app

For viewing fish survival and movement simulations based on current conditions, visit out SHINY app:

[CalFishTrack SHINY app](http://oceanview.pfeg.noaa.gov/shiny/FED/CalFishTrack)

<br />

## Project Reports

None currently available.

<br />

## Study Area




#### Map of receiver and release locations in the Central Valley

```{r map 1, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/JSATS_Full.png"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```

<br />

#### Closeup map of receiver locations in the Sacramento-San Joaquin Delta

```{r map 2, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/JSATS_Delta.png"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```
