---
title: CalFishTrack

output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    includes:
      in_header: GA_Script.html
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
```


#  *Central Valley Enhanced*
#  *Acoustic Tagging Project*
```{r logos, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')

```

<br/>

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

`r anicon::nia("New Updates", size = 2)`

1. [New webpage created for Hatchery Fall-run Chinook salmon Paired releases 3/24/2021](https://calfishtrack.github.io/real-time/pageSLPRFR_2021.html)
2. [New webpage created for 6-Year Study San Joaquin River Steelhead releases 3/23/2021](https://calfishtrack.github.io/real-time/pageSJSTH_2021.html)
3. [New webpage created for Feather River Hatchery Spring-run Chinook salmon releases 3/19/2021](https://calfishtrack.github.io/real-time/pageFHSR_2021.html)
4. [New webpage created for Battle Creek jump-start hatchery winter-run Chinook salmon releases 3/8/2021](https://calfishtrack.github.io/real-time/pageBCJSWR_2021.html)
5. [New webpage created for hatchery winter-run Chinook salmon release 2/1/2021](https://calfishtrack.github.io/real-time/pageLSWR_2021.html)



</div>
    
<br/>

## Background

There is a well documented need for improved detection and associated modeling of salmon migration and survival in the Central Valley. We propose to address this need through an expanded acoustic receiver network and associated real-time and retrospective modeling of the data. The proposed work includes (1) the deployment of real-time receivers that will provide timely information on migrating salmon smolt location and timing, (2) expansion of the existing autonomous acoustic array to increase the coverage and detection efficiency; (3) development of new metrics for the real-time data for key management relevant questions such as entrainment estimates at critical junctions (Georgiana Slough and Delta Cross Channel); and (4) a retrospective analyses directly geared toward improving the quality and robustness of an existing forecasting model -- the NMFS enhanced particle tracking model.

<br />

## Statement of Research

The San Francisco Bay-Delta is both the hub for the infrastructure for California&rsquo;s water supply and critical migratory and rearing habitat for four native runs of Chinook salmon. Understanding salmon survival and migration dynamics in the Delta and its tributaries is critical to the operation of state and federal water projects, recovery of ESA-listed species, and sport and commercial fisheries management. Tracking the fate of individual tagged fish can be accomplished with acoustic tagging (AT), tracking groups of AT fish can be used to develop estimates of survival and movement for other non-AT fish also part of that group, and population level sampling programs can use survival estimates generated by AT and applied to other mass marked (coded wire tagging; CWT) groups to develop improved capture efficiency for these sampling programs.  These capture efficiency estimates can then be used to estimate abundance of non-tagged populations. 

<br />

## Research Objectives 

This work will have significant implications for understanding movement, distribution, and survival of all four runs of Central Valley Chinook salmon. For more information on specific runs and the real-time tracking of these fish, click on a link in the drop-down "Study Population Detections" menu.

<br />

## How to have your data hosted here

Every year, telemetry researchers from multiple organizations and agencies utilize the receivers deployed and data tools developed as part of this project. We request that if there is interest is utilizing these resources, please do the following things:

* Prior to purchasing your tags, coordinate tag codes with the tag code coordinator (Arnold Ammann <arnold.ammann@noaa.gov>).

* Prior to your study's releases, fill out this [summary form](https://github.com/CalFishTrack/real-time/blob/master/data/Telemetry_Study_Summary_Framework_BlankTemplate.docx?raw=true) and send to the website administrator (Cyril Michel <cyril.michel@noaa.gov>).

* Once fish are released, send the website administrator (Cyril Michel <cyril.michel@noaa.gov>) your tagging data in a text or csv format, following [this template](https://github.com/CalFishTrack/real-time/blob/master/data/tagging_data_template.txt?raw=true). Please observe the same formatting as in the tempate.

<br />

## Receiver deployments

For more information on where and when receivers are deployed, visit our receiver deployment page:

[Receiver Deployments](https://calfishtrack.github.io/real-time/pageDEPLOY.html)

<br />


## Detection Data

For downloading real-time detection data and archived detection data from the entire receiver array, visit our Data download page:

[Download Data](https://calfishtrack.github.io/real-time/pageRealtime_download.html)

<br />

## STARS Shiny app

For viewing fish survival and movement predictions based on current river conditions, visit our SHINY app:

[STARS Shiny app](http://oceanview.pfeg.noaa.gov/shiny/FED/CalFishTrack)

<br />

## Related Reports and Publications

[Ammann, A.J. Factors affecting detection probability and range of transmitters and receivers designed for the Juvenile Salmon Acoustic Telemetry System. Environ Biol Fish 103, 625–634 (2020).](https://doi.org/10.1007/s10641-020-00987-4)

[Notch, J.J., McHuron, A.S., Michel, C.J. et al. Outmigration survival of wild Chinook salmon smolts through the Sacramento River during historic drought and high water conditions. Environ Biol Fish 103, 561–576 (2020).](https://doi.org/10.1007/s10641-020-00952-1)

[Notch, J., R. Robinson, T. Pham, R. Logston, A. McHuron, A. Ammann, C. Michel. 2020. Enhanced Acoustic Tagging, Analysis, and Real-Time Monitoring of Wild and Hatchery Salmonids in the Sacramento River Valley – 2019 annual report. Report prepared by University of California – Santa Cruz for the U.S. Bureau of Reclamation under contract USDI/BOR# R18AC00039.](https://github.com/CalFishTrack/real-time/blob/master/data/UCSC_AT_BOR yearly_report_2019_final.pdf?raw=true)

<br />
