---
title: |
  | Central Valley Enhanced
  | Acoustic Tagging Project
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(knitr)
library(kableExtra)
```

```{r logos, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')
```

<br/>
<br/>

```{r spring run pic, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/RBDD.jpg"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```
<br/>
<br/>

# *Sacramento River wild Chinook salmon from Red Bluff Diversion Dam Screw Traps*

<br/>

## 2017-2018 Season (PROVISIONAL DATA)
<br/>


Chinook salmon stock assignments not currently available, but likely a combination of fall and spring-run fish

<br/>

## Project Status

PROJECT IS COMPLETE, ALL TAGS ARE NO LONGER ACTIVE

Project has begun, see tagging details below:
```{r print table with fish release details, echo = FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")
latest <- read.csv("latest_download.csv", stringsAsFactors = F)


study_tagcodes <- tagcodes[tagcodes$StudyID == "RBDD-2018",]
study_tagcodes$Release_week <- NA

study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-12"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-12") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-20") & study_tagcodes$RelDT < as.POSIXct("2018-05-24"), "Release_week"] <- "Week 3"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-24") & study_tagcodes$RelDT < as.POSIXct("2018-06-01"), "Release_week"] <- "Week 4"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-06-01") & study_tagcodes$RelDT < as.POSIXct("2018-06-07"), "Release_week"] <- "Week 5"


release_stats <- aggregate(list(First_release_time = study_tagcodes$RelDT),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = min)
release_stats <- merge(release_stats,
                       aggregate(list(Last_release_time = study_tagcodes$RelDT),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = max),
                       by = c("Release_week"))

                           
release_stats <- merge(release_stats, aggregate(list(Number_fish_released =
                                                       study_tagcodes$TagID_Hex),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {length(unique(x))}),
                       by = c("Release_week"))

release_stats <- merge(release_stats,
                       aggregate(list(Release_location = study_tagcodes$Rel_loc),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Release_rkm = study_tagcodes$Rel_rkm),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_length = study_tagcodes$Length),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = mean),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_weight = study_tagcodes$Weight),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = mean),
                       by = c("Release_week"))

release_stats[,c("Mean_length", "Mean_weight")] <- round(release_stats[,c("Mean_length", "Mean_weight")],1)

kable(release_stats, format = "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
                       

```

<br/>

## Real-time Fish Detections

*Sacramento real-time receivers deployed 2018-02-01, Georgiana_Slough and Sac_BlwGeorgiana receivers deployed 2018-04-16, data current as of `r latest`. All times in Pacific Standard Time.*

<br/>
<center>
#### Detections at Tower Bridge (downtown Sacramento) versus Sacramento River flows at Wilkins Slough
</center>

```{r print figure of fish detections at Tower, echo = FALSE, message = FALSE, fig.height = 6, fig.width = 10}

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(CDECRetrieve)
library(reshape2)

detects_study <- read.csv("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = F)
detects_study$DateTime_PST <- as.POSIXct(detects_study$DateTime_PST, format = "%Y-%m-%d %H:%M:%S", "Etc/GMT+8")

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %H:%M:%S %p", tz = "Etc/GMT+8")

tagcodes$Release_week <- NA
tagcodes[tagcodes$RelDT < as.POSIXct("2018-05-12"), "Release_week"] <- "Week 1"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-05-12") & tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 2"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-05-20") & tagcodes$RelDT < as.POSIXct("2018-05-24"), "Release_week"] <- "Week 3"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-05-24") & tagcodes$RelDT < as.POSIXct("2018-06-01"), "Release_week"] <- "Week 4"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-06-01") & tagcodes$RelDT < as.POSIXct("2018-06-07"), "Release_week"] <- "Week 5"

#wlk_flow <- read.csv("wlk.csv")

if (nrow(detects_study) == 0){
  "No detections yet"
} else {
  
  detects_study <- detects_study[detects_study$general_location == "TowerBridge",]
  detects_study <- merge(detects_study,aggregate(list(first_detect = detects_study$DateTime_PST), by = list(TagCode= detects_study$TagCode), FUN = min))
  
  detects_study$Day <- as.Date(detects_study$first_detect, "Etc/GMT+8")
  
  detects_study <- merge(detects_study, tagcodes[,c("TagID_Hex", "RelDT", "StudyID", "Release_week", "tag_life")], by.x = "TagCode", by.y = "TagID_Hex")
  
  starttime <- as.Date(min(detects_study$RelDT), "Etc/GMT+8")
  endtime <- min(as.Date(c(Sys.time())), max(as.Date(detects_study$RelDT)+detects_study$tag_life))
  

  wlk_flow <- cdec_query("WLK", "20", "H", starttime, endtime+1)

  wlk_flow$datetime <- as.Date(wlk_flow$datetime)
  wlk_flow_day <- aggregate(list(parameter_value = wlk_flow$parameter_value),
                            by = list(Day = wlk_flow$datetime),
                            FUN = mean, na.rm = T)


  daterange <- data.frame(Day = seq.Date(from = starttime, to = endtime, by = "day"))

  rels <- unique(tagcodes[tagcodes$StudyID == unique(detects_study$StudyID), "Release_week"])
  rel_num <- length(rels)
  rels_no_detects <- as.character(rels[!(rels %in% unique(detects_study$Release_week))])

  tagcount <- aggregate(list(unique_tags = detects_study$TagCode), by = list(Day = detects_study$Day, Release_week = detects_study$Release_week ), FUN = function(x){length(unique(x))})
  tagcount1 <- reshape2::dcast(tagcount, Day ~ Release_week)

  daterange1 <- merge(daterange, tagcount1, all.x=T)

  if(length(rels_no_detects)>0){
    for(i in rels_no_detects){
      daterange1 <- cbind(daterange1, x=NA)
      names(daterange1)[names(daterange1) == 'x'] <- paste(i)
    }
  }

  daterange2 <- merge(daterange1, wlk_flow_day, by = "Day", all.x = T)

  rownames(daterange2) <- daterange2$Day
  daterange2$Day <- NULL

  par(mar=c(6, 5, 2, 5) + 0.1)
  barp <- barplot(t(daterange2[,1:ncol(daterange2)-1]), plot = FALSE, beside = T)
  barplot(t(daterange2[,1:ncol(daterange2)-1]), beside = T, col=rainbow(rel_num),
          xlab = "", ylab = "Number of fish arrivals per day",
          ylim = c(0,max(daterange2[,1:ncol(daterange2)-1], na.rm = T)*1.2),
          las = 2, xlim=c(0,max(barp)+1), cex.lab = 1.5, yaxt = "n", xaxt = "n", border=NA)#,
  #legend.text = colnames(daterange2[,1:ncol(daterange2)-1]),
  #args.legend = list(x ='topright', bty='n', inset=c(-0.2,0)), title = "Release Group")
  legend(x ='topleft', legend = colnames(daterange2)[1:ncol(daterange2)-1], fill= rainbow(rel_num), horiz = T, title = "Release Week")
  ybreaks <- if(max(daterange2[,1:ncol(daterange2)-1], na.rm = T) < 4) {max(daterange2[,1:ncol(daterange2)-1], na.rm = T)} else {5}
  xbreaks <- if(ncol(barp) > 10) {seq(1, ncol(barp), 2)} else {1:ncol(barp)}
  barpmeans <- colMeans(barp)
  axis(1, at = barpmeans[xbreaks], labels = rownames(daterange2[xbreaks,]), las = 2)
  axis(2, at = pretty(0:max(daterange2[,1:ncol(daterange2)-1], na.rm = T), ybreaks))

  par(new=T)

  plot(x = barpmeans, daterange2$parameter_value, yaxt = "n", xaxt = "n", ylab = "", xlab = "", col = "blue", type = "l", lwd=2, xlim=c(0,max(barp)+1), ylim = c(min(daterange2$parameter_value, na.rm = T), max(daterange2$parameter_value, na.rm=T)*1.1))#, ylab = "Returning adults", xlab= "Outmigration year", yaxt="n", col="red", pch=20)
  axis(side = 4)#, labels = c(2000:2016), at = c(2000:2016))
  mtext("Flow (cfs) at Wilkins Slough", side=4, line=3, cex=1.5, col="blue")
}

```

<br/>
<br/>

<center>
#### Detections at Benicia Bridge
</center>

```{r print figure of fish detections, echo = FALSE, message = FALSE, fig.height = 6, fig.width = 10}

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

#library(CDECRetrieve)
library(reshape2)

detects_study <- read.csv("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = F)

detects_study$DateTime_PST <- as.POSIXct(detects_study$DateTime_PST, format = "%Y-%m-%d %H:%M:%S", "Etc/GMT+8")

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

detects_study <- detects_study[detects_study$general_location %in% c("Benicia_west", "Benicia_east"),]

if (nrow(detects_study)>0) {
  detects_study <- merge(detects_study,aggregate(list(first_detect = detects_study$DateTime_PST), by = list(TagCode= detects_study$TagCode), FUN = min))
  
  detects_study$Day <- as.Date(detects_study$first_detect, "Etc/GMT+8")
  
  detects_study <- merge(detects_study, tagcodes[,c("TagID_Hex", "RelDT", "StudyID")], by.x = "TagCode", by.y = "TagID_Hex")
  
  starttime <- as.Date(min(detects_study$RelDT), "Etc/GMT+8")
  #endtime <- as.Date(c(Sys.time()))#, max(detects_study$first_detect)+60*60*24)))
  #wlk_flow <- cdec_query("COL", "20", "H", starttime, endtime+1)
  #wlk_flow$datetime <- as.Date(wlk_flow$datetime)
  #wlk_flow_day <- aggregate(list(parameter_value = wlk_flow$parameter_value), by = list(Day = wlk_flow$datetime), FUN = mean, na.rm = T)
  
  daterange <- data.frame(Day = seq.Date(from = starttime, to = endtime, by = "day"))
  
  rels <- unique(tagcodes[tagcodes$StudyID == unique(detects_study$StudyID), "RelDT"])
  rel_num <- length(rels)
  rels_no_detects <- as.character(rels[!(rels %in% unique(detects_study$RelDT))])
  
  tagcount <- aggregate(list(unique_tags = detects_study$TagCode), by = list(Day = detects_study$Day, RelDT = detects_study$RelDT ), FUN = function(x){length(unique(x))})
  tagcount1 <- reshape2::dcast(tagcount, Day ~ RelDT)
                    
  daterange1 <- merge(daterange, tagcount1, all.x=T)
  
  if(length(rels_no_detects)>0){
    for(i in rels_no_detects){
      daterange1 <- cbind(daterange1, x=NA)
      names(daterange1)[names(daterange1) == 'x'] <- paste(i)
    }
  }
  
  #daterange2 <- merge(daterange1, wlk_flow_day, by = "Day", all.x = T)
  daterange2 <- daterange1
  
  rownames(daterange2) <- daterange2$Day
  daterange2$Day <- NULL
  
  par(mar=c(6, 5, 2, 5) + 0.1)
  barp <- barplot(t(daterange2[,1:ncol(daterange2)]), plot = FALSE, beside = T)
  barplot(t(daterange2[,1:ncol(daterange2)]), beside = T, col=rainbow(rel_num), 
          xlab = "", ylab = "Number of fish arrivals per day", 
          ylim = c(0,max(daterange2[,1:ncol(daterange2)], na.rm = T)*1.2), 
          las = 2, xlim=c(0,max(barp)+1), cex.lab = 1.5, yaxt = "n", xaxt = "n")#, 
          #legend.text = colnames(daterange2[,1:ncol(daterange2)-1]),
          #args.legend = list(x ='topright', bty='n', inset=c(-0.2,0)), title = "Release Group")
  legend(x ='topleft', legend = colnames(daterange2[,1:ncol(daterange2)]), fill= rainbow(rel_num), horiz = T, title = "Release Group")
  ybreaks <- if(max(daterange2[,1:ncol(daterange2)], na.rm = T) < 4) {max(daterange2[,1:ncol(daterange2)], na.rm = T)} else {5}
  xbreaks <- if(ncol(barp) > 10) {seq(1, ncol(barp), 2)} else {1:ncol(barp)}
  barpmeans <- colMeans(barp)
  axis(1, at = barpmeans[xbreaks], labels = rownames(daterange2[xbreaks,]), las = 2)
  axis(2, at = pretty(0:max(daterange2[,1:ncol(daterange2)], na.rm = T), ybreaks))
  box()

#par(new=T)

#plot(x = barpmeans, daterange2$parameter_value, yaxt = "n", xaxt = "n", ylab = "", xlab = "", col = "blue", type = "l", lwd=2, xlim=c(0,max(barp)+1), ylim = c(min(daterange2$parameter_value, na.rm = T), max(daterange2$parameter_value, na.rm=T)*1.1))#, ylab = "Returning adults", xlab= "Outmigration year", yaxt="n", col="red", pch=20)
#axis(side = 4)#, labels = c(2000:2016), at = c(2000:2016))
#mtext("Flow (cfs) at Colusa Bridge", side=4, line=3, cex=1.5, col="blue")

}else{
  print("No detections at Benicia yet")
}

```


<br/>
<br/>

</center>
#### Minimum survival to Tower Bridge (using CJS survival model)
</center>

<br/>

```{r print table of survival, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)
library(RMark)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "RBDD-2018",]
study_tagcodes$Release_week <- NA
study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-12"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-12") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-20") & study_tagcodes$RelDT < as.POSIXct("2018-05-24"), "Release_week"] <- "Week 3"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-24") & study_tagcodes$RelDT < as.POSIXct("2018-06-01"), "Release_week"] <- "Week 4"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-06-01") & study_tagcodes$RelDT < as.POSIXct("2018-06-07"), "Release_week"] <- "Week 5"

study_count <- nrow(study_tagcodes)

if (nrow(test) == 0){
  "No detections yet"
} else {
  
  test <- merge(test, study_tagcodes[,c("TagID_Hex", "Release_week")], by.x = "TagCode", by.y = "TagID_Hex")
  
  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  
  ## Only do survival to Sac for now
  test <- test[test$rkm > 160,]
  
  ## Create inp for survival estimation
  
  inp <- as.data.frame(reshape2::dcast(test, TagCode ~ rkm, fun.aggregate = length))
  
  ## Sort columns by river km in descending order
  # Count number of genlocs
  gen_loc_sites <- ncol(inp)-1
  
  if(gen_loc_sites <2){
    "Detections at only one location so far, survival cannot yet be estimated"
  }else{
  
    inp <- inp[,c(1,order(names(inp[,2:(gen_loc_sites+1)]), decreasing = T)+1)]
  
    inp <- merge(study_tagcodes, inp, by.x = "TagID_Hex", by.y = "TagCode", all.x = T)
    
    inp2 <- inp[,(ncol(inp)-gen_loc_sites+1):ncol(inp)]
    inp2[is.na(inp2)] <- 0
    inp2[inp2 > 0] <- 1
    
    inp <- cbind(inp, inp2)
    groups <- as.character(sort(unique(inp$Release_week)))
  
    inp[,groups] <- 0
    for (i in groups) {
      inp[as.character(inp$Release_week) == i, i] <- 1
    }
    
    inp$inp_final <- paste("1",apply(inp2, 1, paste, collapse=""), " ",apply(inp[,groups], 1, paste, collapse=" ")," ;",sep = "")
    
    
    write.table(inp$inp_final,"WRinp.inp",row.names = F, col.names = F, quote = F)
    
    WRinp <- convert.inp("WRinp.inp", group.df=data.frame(rel=groups))
    
    WR.process <- process.data(WRinp, model="CJS", begin.time=1, groups = "rel") 
    
    WR.ddl <- make.design.data(WR.process)
    
    WR.mark.all <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time),p=list(formula=~time)), silent = T, output = F)
    
    WR.mark.rel <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time*rel),p=list(formula=~time)), silent = T, output = F)
    
    WR.surv <- round(WR.mark.all$results$real[1,c("estimate", "se", "lcl", "ucl")] * 100,1)
    WR.surv <- rbind(WR.surv, round(WR.mark.rel$results$real[seq(from=1,to=length(groups)*2,by = 2),c("estimate", "se", "lcl", "ucl")] * 100,1))
    WR.surv$Detection_efficiency <- NA
    WR.surv[1,"Detection_efficiency"] <- round(WR.mark.all$results$real[gen_loc_sites+1,"estimate"] * 100,1)
    
    WR.surv <- cbind(c("ALL", groups), WR.surv)
    
    colnames(WR.surv) <- c("Release Week", "Survival (%)", "SE", "95% lower C.I.", "95% upper C.I.", "Detection efficiency (%)")
    
    print(kable(WR.surv, row.names = F, "html") %>%
            kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
  }
}

cleanup(ask = F)

```    

<br/>
<br/>

</center>
#### Reach-specific survival and probability of entering Georgiana Slough
</center>

<br/>

```{r print table of survival and routing, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)
library(RMark)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "RBDD-2018",]
study_tagcodes$Release_week <- NA
study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-12"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-12") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-20") & study_tagcodes$RelDT < as.POSIXct("2018-05-24"), "Release_week"] <- "Week 3"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-24") & study_tagcodes$RelDT < as.POSIXct("2018-06-01"), "Release_week"] <- "Week 4"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-06-01") & study_tagcodes$RelDT < as.POSIXct("2018-06-07"), "Release_week"] <- "Week 5"

study_count <- nrow(study_tagcodes)

if (nrow(test) == 0){
  "No detections yet"
} else {
  
  test <- merge(test, study_tagcodes[,c("TagID_Hex", "Release_week")], by.x = "TagCode", by.y = "TagID_Hex")
  
  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  
  ## Only do survival to Georg split for now
  test <- test[test$general_location %in% c("TowerBridge", "I80-50_Br", "Sac_BlwGeorgiana", "Sac_BlwGeorgiana2", "Georgiana_Slough1", "Georgiana_Slough2"),]
  
  ## We can only do multistate model if there is at least one detection in each route
  
  if(nrow(test[test$general_location %in% c("Sac_BlwGeorgiana", "Sac_BlwGeorgiana2"),]) == 0 |
     nrow(test[test$general_location %in% c("Georgiana_Slough1", "Georgiana_Slough2"),]) == 0){
    "Too few detections: routing probability cannot be estimated"
  }else{
    
    ## Make a crosstab query with frequencies for all tag/location combination
    test$general_location <- factor(test$general_location, levels = c("TowerBridge", "I80-50_Br", "Sac_BlwGeorgiana", "Sac_BlwGeorgiana2", "Georgiana_Slough1", "Georgiana_Slough2"))
    test$TagCode <- factor(test$TagCode, levels = study_tagcodes$TagID_Hex)
    mytable <- table(test$TagCode, test$general_location) # A will be rows, B will be columns
    
    ## Change all frequencies bigger than 1 to 1. Here you could change your minimum cutoff to 2 detections, and then make another command that changes all detections=1 to 0
    mytable[mytable>0] <- "A"
    
    ## Order in order of rkm
    mytable2 <- mytable[, c("TowerBridge", "I80-50_Br", "Sac_BlwGeorgiana", "Sac_BlwGeorgiana2", "Georgiana_Slough1", "Georgiana_Slough2")]
    
    ## Now sort the crosstab rows alphabetically
    mytable2 <- mytable2[order(row.names(mytable2)),]
    
    mytable2[which(mytable2[, "Sac_BlwGeorgiana"]=="1"), "Sac_BlwGeorgiana"] <- "A"
    mytable2[which(mytable2[, "Sac_BlwGeorgiana2"]=="1"), "Sac_BlwGeorgiana2"] <- "A"
    mytable2[which(mytable2[, "Georgiana_Slough1"]=="1"), "Georgiana_Slough1"] <- "B"
    mytable2[which(mytable2[, "Georgiana_Slough2"]=="1"), "Georgiana_Slough2"] <- "B"
    
    ## Make a crosstab query with frequencies for all weekly release groups
    test$Release_week <- factor(test$Release_week)
    mytable3 <- table(test$TagCode, test$Release_week) # A will be rows, B will be columns
    
    ## Change all frequencies bigger than 1 to 1. Here you could change your minimum cutoff to 2 detections, and then make another command that changes all detections=1 to 0
    mytable3[mytable3>0] <- 1
    
    ## Order in order of rkm
    mytable4 <- mytable3[, order(colnames(mytable3))]
    
    ## Now sort the crosstab rows alphabetically
    mytable4 <- mytable4[order(row.names(mytable2)),]
    
    ## Now order the study_tagcodes table the same way
    study_tagcodes <- study_tagcodes[order(study_tagcodes$TagID_Hex),]
    
    ## Paste together (concatenate) the data from each column of the crosstab into one string per row, add to tagging_meta.
    ## For this step, make sure both are sorted by FishID
    study_tagcodes$inp_part1 <- apply(mytable2[,1:2],1,paste,collapse="")
    study_tagcodes$inp_partA <- apply(mytable2[,3:4],1,paste,collapse="")
    study_tagcodes$inp_partB <- apply(mytable2[,5:6],1,paste,collapse="")
    study_tagcodes$inp_group <- apply(mytable4,1,paste,collapse=" ")
    
    ## We need to have a way of picking which route to assign to a fish if it was detected by both georg and blw-georg recvs
    ## We will say that the last detection at that junction is what determines the route it took
    
    ## find last detection at each genloc
    departure <- aggregate(list(depart = test$DateTime_PST), by = list(TagID_Hex = test$TagCode, last_location = test$general_location), FUN = max)
    ## subset for just juncture locations
    departure <- departure[departure$general_location %in% c("Sac_BlwGeorgiana", "Sac_BlwGeorgiana2", "Georgiana_Slough1", "Georgiana_Slough2"),]
    ## Find genloc of last known detection
    last_depart <- departure[which.max(departure$depart),]
    study_tagcodes <- merge(study_tagcodes, last_depart[,c("TagID_Hex", "last_location")], by = "TagID_Hex", all.x = T)
    
    ## Assume that the Sac is default pathway, and for fish that were detected in neither route, it would get a "00" in inp so doesn't matter anyway
    study_tagcodes$inp_final <- paste("A",study_tagcodes$inp_part1, study_tagcodes$inp_partA," 1 ;", sep = "")
    
    ## now put in exceptions...fish that were seen in georgiana last
    study_tagcodes[study_tagcodes$last_location %in% c("Georgiana_Slough1", "Georgiana_Slough2"), "inp_final"] <- paste("A",study_tagcodes$inp_part1, study_tagcodes$inp_partB," 1 ;", sep = "")
    
    write.table(study_tagcodes$inp_final,"WRinp_multistate.inp",row.names = F, col.names = F, quote = F)
    
    WRinp <- convert.inp("WRinp_multistate.inp")
    
    dp <- process.data(WRinp, model="Multistrata") 
    
    ddl <- make.design.data(dp)
    
    #### p ####
    # Can't be seen at 2B or 3B (tower or I80)
    ddl$p$fix=NA
    ddl$p$fix[ddl$p$stratum == "B" & ddl$p$time %in% c(2,3)]=0
    
    #### Psi ####
    # Only 1 transition allowed:
    # from A to B at time interval 3 to 4
    
    ddl$Psi$fix=0
    # A to B can only happen for interval 2-3
    ddl$Psi$fix[ddl$Psi$stratum=="A"&
                  ddl$Psi$tostratum=="B" & ddl$Psi$time==3]=NA
    
    #### Phi a.k.a. S ####
    ddl$S$fix=NA
    # None in B for reaches 1,2,3 and fixing it to 1 for 4 (between two georg lines). All getting fixed to 1
    ddl$S$fix[ddl$S$stratum=="B" & ddl$S$time %in% c(1,2,3,4)]=1
    
    # For route A, fixing it to 1 for 4 (between two blw_georg lines)
    ddl$S$fix[ddl$S$stratum=="A" & ddl$S$time==4]=1
    ## We use -1 at beginning of formula to remove intercept. This is because different routes probably shouldn't share the same intercept
    
    p.timexstratum=list(formula=~-1+stratum:time)
    Psi.stratumxtime=list(formula=~-1+stratum:time)
    S.stratumxtime=list(formula=~-1+stratum:time)
    
    ## Run model a first time
    S.timexstratum.p.timexstratum.Psi.timexstratum=mark(dp,ddl, model.parameters=list(S=S.stratumxtime,p= p.timexstratum,Psi=Psi.stratumxtime), realvcv = T)
    
    ## Identify any parameter estimates at 1, which would likely have bad SE estimates.
    profile.intervals <- which(S.timexstratum.p.timexstratum.Psi.timexstratum$results$real$estimate %in% c(0,1) & !S.timexstratum.p.timexstratum.Psi.timexstratum$results$real$fixed == "Fixed")
    
    ## Rerun model using profile interval estimation for the tricky parameters
    S.timexstratum.p.timexstratum.Psi.timexstratum=mark(dp,ddl, model.parameters=list(S=S.stratumxtime,p= p.timexstratum,Psi=Psi.stratumxtime), realvcv = T, profile.int = profile.intervals)
    
    results <- S.timexstratum.p.timexstratum.Psi.timexstratum$results$real
    
    results_short <- results[rownames(results) %in% c("S sA g1 c1 a0 o1 t1",
                                                      "S sA g1 c1 a1 o2 t2",
                                                      "S sA g1 c1 a2 o3 t3",
                                                      "p sA g1 c1 a1 o1 t2",
                                                      "p sA g1 c1 a2 o2 t3",
                                                      "p sA g1 c1 a3 o3 t4",
                                                      "p sB g1 c1 a3 o3 t4",
                                                      "Psi sA toB g1 c1 a2 o3 t3"
                                                      ),]
    
    
    results_short <- round(results_short[,c("estimate", "se", "lcl", "ucl")] * 100,1)
    
    results_short$Measure <- c("Survival from release to TowerBridge", "Survival from TowerBridge to I80-50_Br", "Survival from I80-50_Br to Georgiana Slough confluence",
                               "Detection probability at TowerBridge", "Detection probability at I80-50_Br", "Detection probability at Blw_Georgiana", "Detection probability at Georgiana Slough",
                               "Routing probability into Georgiana Slough")
    
    results_short <- results_short[,c("Measure", "estimate", "se", "lcl", "ucl")]

    print(kable(results_short, row.names = F, "html") %>%
            kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
  }
}

cleanup(ask = F)
```

<br/>
<br/>

<center>
#### Minimum survival to Benicia Bridge East Span (using CJS survival model)
</center>

<br/>

```{r print table of survival to Benicia, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
library(data.table)
library(RMark)

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "RBDD-2018",]
study_count <- nrow(study_tagcodes)

test <- merge(test, tagcodes[,c("TagID_Hex", "RelDT")], by.x = "TagCode", by.y = "TagID_Hex")

detects_benicia <- detects_study[detects_study$general_location %in% c("Benicia_west", "Benicia_east"),]

if (nrow(detects_benicia) == 0){
  "No detections yet"
} else {
  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  
  ## Only do survival to Benicia here
  test <- test[test$rkm < 53,]
  
  ## Create inp for survival estimation
  
  inp <- as.data.frame(reshape2::dcast(test, TagCode ~ rkm, fun.aggregate = length))
  
  ## Sort columns by river km in descending order
  # Count number of genlocs
  gen_loc_sites <- ncol(inp)-1
  
  inp <- inp[,c(1,order(names(inp[,2:(gen_loc_sites+1)]), decreasing = T)+1)]
  WR_tagcodes <- tagcodes[tagcodes$StudyID == "Nimbus-Fall-2018",]
  inp <- merge(WR_tagcodes, inp, by.x = "TagID_Hex", by.y = "TagCode", all.x = T)
  
  inp2 <- inp[,(ncol(inp)-gen_loc_sites+1):ncol(inp)]
  inp2[is.na(inp2)] <- 0
  inp2[inp2 > 0] <- 1
  
  inp <- cbind(inp, inp2)
  groups <- as.character(sort(unique(inp$RelDT)))

  inp[,groups] <- 0
  for (i in groups) {
    inp[as.character(inp$RelDT) == i, i] <- 1
  }
  
  if(length(groups) > 1){
    inp$inp_final <- paste("1",apply(inp2, 1, paste, collapse=""), " ",apply(inp[,groups], 1, paste, collapse=" ")," ;",sep = "")
  }else{
    inp$inp_final <- paste("1",apply(inp2, 1, paste, collapse=""), " ",inp[,groups]," ;",sep = "")
  }
  
  
  write.table(inp$inp_final,"WRinp.inp",row.names = F, col.names = F, quote = F)
  
  if(length(groups) > 1){
  
    WRinp <- convert.inp("WRinp.inp", group.df=data.frame(rel=groups))
    WR.process <- process.data(WRinp, model="CJS", begin.time=1, groups = "rel") 
    
    WR.ddl <- make.design.data(WR.process)
    
    WR.mark.all <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time),p=list(formula=~time)), silent = T, output = F)
    
    WR.mark.rel <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time*rel),p=list(formula=~time)), silent = T, output = F)
    
    WR.surv <- round(WR.mark.all$results$real[1,c("estimate", "se", "lcl", "ucl")] * 100,1)
    WR.surv <- rbind(WR.surv, round(WR.mark.rel$results$real[seq(from=1,to=length(groups)*2,by = 2),c("estimate", "se", "lcl", "ucl")] * 100,1))
    
  }else{
    
    WRinp <- convert.inp("WRinp.inp")
    WR.process <- process.data(WRinp, model="CJS", begin.time=1) 
    
      
    WR.ddl <- make.design.data(WR.process)
    
    WR.mark.all <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time),p=list(formula=~time)), silent = T, output = F)

    WR.surv <- round(WR.mark.all$results$real[1,c("estimate", "se", "lcl", "ucl")] * 100,1)
    
  }
  
  WR.surv$Detection_efficiency <- NA
  WR.surv[1,"Detection_efficiency"] <- round(WR.mark.all$results$real[gen_loc_sites+1,"estimate"] * 100,1)
    
  WR.surv <- cbind(c("ALL", groups), WR.surv)
  
  colnames(WR.surv) <- c("Release Group", "Survival (%)", "SE", "95% lower C.I.", "95% upper C.I.", "Detection efficiency (%)")
  
  print(kable(WR.surv, row.names = F, "html") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))

}

cleanup(ask = F)

```    


<br/>
<br/>

<center>
#### Detections statistics at all realtime receivers
</center>

<br/>

```{r print tables of fish detections, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_RBDD-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "RBDD-2018",]
study_tagcodes$Release_week <- NA
study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-12"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-12") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-20") & study_tagcodes$RelDT < as.POSIXct("2018-05-24"), "Release_week"] <- "Week 3"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-24") & study_tagcodes$RelDT < as.POSIXct("2018-06-01"), "Release_week"] <- "Week 4"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-06-01") & study_tagcodes$RelDT < as.POSIXct("2018-06-07"), "Release_week"] <- "Week 5"

study_count <- nrow(study_tagcodes)

if (nrow(test) == 0){
  "No detections yet"
} else {
  
  test <- merge(test, study_tagcodes[,c("TagID_Hex", "Release_week")], by.x = "TagCode", by.y = "TagID_Hex")

  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  tag_stats <- aggregate(list(First_arrival = test$DateTime_PST), 
                         by= list(general_location = test$general_location),
                         FUN = min)
  tag_stats <- merge(tag_stats, 
                     aggregate(list(Mean_arrival = test$DateTime_PST), 
                         by= list(general_location = test$general_location),
                         FUN = mean), 
                     by = c("general_location"))
  tag_stats <- merge(tag_stats, 
                     aggregate(list(Fish_count = test$TagCode), 
                         by= list(general_location = test$general_location), 
                         FUN = function(x) {length(unique(x))}), 
                     by = c("general_location"))
  tag_stats$Percent_arrived <- round(tag_stats$Fish_count/study_count * 100,2)
      
  tag_stats <- merge(tag_stats, unique(gen_locs[,c("general_location", "rkm")]))
  
  tag_stats <- tag_stats[order(tag_stats$rkm, decreasing = T),]
  
  print(kable(tag_stats, row.names = F, 
              caption = "Detections for all release weeks combined",
              "html") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
  
  for (j in sort(unique(study_tagcodes$Release_week))) {
    
    if(nrow(test[test$Release_week == j,]) > 0 ) {
    
      temp <- test[test$Release_week == j,]
  
      rel_count <- nrow(study_tagcodes[study_tagcodes$Release_week == j,])
  
      tag_stats1 <- aggregate(list(First_arrival = temp$DateTime_PST), 
                             by= list(general_location = temp$general_location), 
                             FUN = min)
      tag_stats1 <- merge(tag_stats1, 
                         aggregate(list(Mean_arrival = temp$DateTime_PST), 
                             by= list(general_location = temp$general_location), 
                             FUN = mean), 
                         by = c("general_location"))
      tag_stats1 <- merge(tag_stats1, 
                         aggregate(list(Fish_count = temp$TagCode), 
                                   by= list(general_location = temp$general_location), 
                                   FUN = function(x) {length(unique(x))}), 
                         by = c("general_location"))
      
      tag_stats1$Percent_arrived <- round(tag_stats1$Fish_count/rel_count * 100,2)
    
      tag_stats1 <- merge(tag_stats1, unique(gen_locs[,c("general_location", "rkm")]))
    
      tag_stats1 <- tag_stats1[order(tag_stats1$rkm, decreasing = T),]
    
      final_stats <- kable(tag_stats1, row.names = F, 
            caption = paste("Detections for",j,"release groups", sep = " "),
            "html")
      print(kable_styling(final_stats, bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
      
    } else {
      cat("\n\n\\pagebreak\n")
      print(paste("No detections for",j,"release group yet", sep=" "), quote = F)
      cat("\n\n\\pagebreak\n")
    }
  }
}

```
