---
title: |
  | Central Valley Enhanced
  | Acoustic Tagging Project
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(knitr)
library(kableExtra)
```

```{r logos, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')

```


<br/>
<br/>

```{r sturgeon pic, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/Juvenile_Green_Sturgeon_crop.jpg"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```
<br/>
<br/>



# *Sacramento River Green Sturgeon*


<br/>

## 2017-2018 Season (PROVISIONAL DATA)
<br/>

## Project Status

PROJECT IS COMPLETE, ALL TAGS ARE NO LONGER ACTIVE

Project has begun, see tagging details below:
```{r print table with fish release details, echo = FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")
latest <- read.csv("latest_download.csv", stringsAsFactors = F)


study_tagcodes <- tagcodes[tagcodes$StudyID == "Juv_Green_Sturgeon_2017",]
release_stats <- aggregate(list(Number_fish_released = study_tagcodes$TagID_Hex),
                           by= list(Release_time = study_tagcodes$RelDT),
                           FUN = function(x) {length(unique(x))}
                           )
release_stats <- merge(release_stats,
                       aggregate(list(Release_location = study_tagcodes$Rel_loc),
                           by= list(Release_time = study_tagcodes$RelDT),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_time"))
release_stats <- merge(release_stats,
                       aggregate(list(Release_rkm = study_tagcodes$Rel_rkm),
                           by= list(Release_time = study_tagcodes$RelDT),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_time"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_length = study_tagcodes$Length),
                           by= list(Release_time = study_tagcodes$RelDT),
                           FUN = mean),
                       by = c("Release_time"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_weight = study_tagcodes$Weight),
                           by= list(Release_time = study_tagcodes$RelDT),
                           FUN = mean),
                       by = c("Release_time"))

release_stats[,c("Mean_length", "Mean_weight")] <- round(release_stats[,c("Mean_length", "Mean_weight")],1)

kable(release_stats, "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
                       

```

<br/>

## Real-time Fish Detections

*Sacramento real-time receivers deployed 2018-02-01, data current as of `r latest`. All times in Pacific Standard Time.*

NOTE: THESE FISH WERE RELEASED SEVERAL MONTHS BEFORE REALTIME STATIONS WERE INSTALLED, THEREFORE DETECTIONS NOTED HERE ARE FOR A SMALL SUBSET OF ALL FISH.

<br/>
<center>
#### Detections at Tower Bridge (downtown Sacramento) versus Sacramento River flows at Colusa Bridge
</center>

```{r print figure of fish detections, echo = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(CDECRetrieve)

detects_study <- read.csv("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_Juv_Green_Sturgeon_2017.csv", stringsAsFactors = F)

if (nrow(detects_study) == 0){
  "No detections yet"
} else {
  detects_study$DateTime_PST <- as.POSIXct(detects_study$DateTime_PST, format = "%Y-%m-%d %H:%M:%S", "Etc/GMT+8")

  detects_study <- merge(detects_study, study_tagcodes[,c("TagID_Hex", "RelDT", "StudyID", "tag_life")], by.x = "TagCode", by.y = "TagID_Hex")


  detects_study <- detects_study[detects_study$general_location == "TowerBridge",]
  detects_study <- merge(detects_study,aggregate(list(first_detect = detects_study$DateTime_PST), by = list(TagCode= detects_study$TagCode), FUN = min))
  
  starttime <- as.Date(min(detects_study$first_detect)-60*60*24, "Etc/GMT+8")
  ## Endtime should be either now, or end of predicted tag life, whichever comes first
  endtime <- min(as.Date(c(Sys.time())), max(as.Date(detects_study$RelDT)+(detects_study$tag_life*1.5)))
  wlk_flow <- cdec_query("COL", "20", "H", starttime, endtime+1)
  wlk_flow$datetime <- as.Date(wlk_flow$datetime)
  wlk_flow_day <- aggregate(list(parameter_value = wlk_flow$parameter_value), by = list(Day = wlk_flow$datetime), FUN = mean, na.rm = T)
  
  detects_study$Day <- as.Date(detects_study$first_detect, "Etc/GMT+8")
  daterange <- data.frame(Day = seq.Date(from = starttime, to = endtime, by = "day"))
  
  
  tagcount <- aggregate(list(unique_tags = detects_study$TagCode), by = list(Day = detects_study$Day), FUN = function(x){length(unique(x))})
  
  daterange1 <- merge(daterange, tagcount, all.x=T)
  daterange2 <- merge(daterange1, wlk_flow_day, by = "Day", all.x = T)
  
  par(mar=c(6, 5, 2, 5) + 0.1)
  barp <- barplot(height= daterange2$unique_tags, plot = FALSE)
  barplot(height= daterange2$unique_tags, col="gray",  names.arg= daterange2$Day, xlab = "", ylab = "Number of fish arrivals per day", ylim = c(0,max(daterange2$unique_tags, na.rm = T)*1.2), las = 2, xlim=c(0,max(barp)+1), cex.lab = 1.5, yaxt = "n", xaxt = "n")
  ybreaks <- if(max(daterange2$unique_tags, na.rm = T) < 4) {max(daterange2$unique_tags, na.rm = T)} else {5}
  xbreaks <- if(length(barp) > 10) {seq(1, length(barp), 5)} else {1:length(barp)}
  axis(1, at = barp[xbreaks], labels = daterange2[xbreaks,"Day"], las = 2)
  axis(2, at = pretty(0:max(daterange2$unique_tags, na.rm = T), ybreaks))
  
  par(new=T)
  
  plot(x = barp, daterange2$parameter_value, yaxt = "n", xaxt = "n", ylab = "", xlab = "", col = "blue", type = "l", lwd=2, xlim=c(0,max(barp)+1))#, ylab = "Returning adults", xlab= "Outmigration year", yaxt="n", col="red", pch=20)
  axis(side = 4)#, labels = c(2000:2016), at = c(2000:2016))
  mtext("Flow (cfs) at Colusa Bridge", side=4, line=3, cex=1.5, col="blue")

}

```

<br/>
<br/>

<center>
#### Detections statistics at all realtime receivers
</center>

```{r print table of fish detections, echo = FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_Juv_Green_Sturgeon_2017.csv", stringsAsFactors = FALSE, colClasses = c(DateTime_PST = "character", RelDT = "character"))
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "Juv_Green_Sturgeon_2017",]
study_count <- nrow(study_tagcodes)

if (nrow(test) == 0){
  "No detections yet"
} else {
  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  tag_stats <- aggregate(list(First_arrival = test$DateTime_PST), 
                         by= list(general_location = test$general_location), FUN = min)
  tag_stats <- merge(tag_stats, 
                     aggregate(list(Fish_count = test$TagCode), 
                         by= list(general_location = test$general_location), 
                         FUN = function(x) {length(unique(x))}), 
                     by = c("general_location"))
  tag_stats$Percent_arrived <- round(tag_stats$Fish_count/study_count * 100,2)
  
  tag_stats <- merge(tag_stats, unique(gen_locs[,c("general_location", "rkm")]))
  
  tag_stats <- tag_stats[order(tag_stats$rkm, decreasing = T),]
  
  kable(tag_stats, row.names = F, "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
}

```
