---
title: CalFishTrack

output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    includes:
      in_header: GA_Script.html
  #prettydoc::html_pretty:
  #  theme: cayman
  #  toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(tidyr)
library(knitr)
library(kableExtra)
library(lubridate)
library(data.table)
library(ggplot2)
#library(xtable)
#library(prettydoc)
library(scales)
library(viridis)
library(forcats)
```

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

<style>
p.caption {
  font-size: 2em;
}
caption {
      font-size: 2em;
}
</style>
#  *Central Valley Enhanced*
#  *Acoustic Tagging Project*
```{r logos, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')
```

<br/>
<br/>

# *Water Year 2021 Survival Summary*

<br/>

```{r pull in latest data download time}

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

latest <- read.csv("latest_download.csv", stringsAsFactors = F)
```

***`r anicon::nia(paste("Study is in progress. Data current as of", latest), size = 1, colour = "red")`
. All times in Pacific Standard Time.***

<br>

## 1.1 Survival to Benicia for all major Chinook salmon tagging efforts (n > 100). 
Hover cursor over points to see release group.
```{r print plot of season total survival, out.extra='style="background-color: #000000; padding:3px"', echo = FALSE, warning=FALSE, message = FALSE}
library(CDECRetrieve)
library(plotly)

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

benicia <- read.csv("benicia_surv.csv", stringsAsFactors = F)
benicia$RelDT <- as.POSIXct(benicia$RelDT)
tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F, colClasses=c("TagID_Hex"="character"))
tol_released <- aggregate(list(total_released = tagcodes$TagID_Hex), by = list(StudyID = tagcodes$StudyID), FUN = length)
benicia <- merge(benicia, tol_released)
## Now remove any release smaller than 100
benicia <- benicia[benicia$total_released >99,]
benicia_rel <- benicia[benicia$Release != "ALL",]
## Now subset to only be WY2021 fish. This usually removes green sturgeon too
benicia_rel <- benicia_rel[benicia_rel$RelDT > "2021-01-01" & benicia_rel$RelDT < "2021-12-01",]
## Remove any steelhead releases
benicia_rel <- benicia_rel[grepl("_SH_", benicia_rel$StudyID) == F,]
benicia_rel <- benicia_rel[grepl("Steelhead", benicia_rel$StudyID) == F,]
### Combine sutter bypass releases
#benicia_rel <- benicia_rel[benicia_rel$StudyID != "SB_Spring_2019",]
#benicia_rel <- rbind(benicia_rel, benicia[benicia$StudyID == "SB_Spring_2019" & benicia$Release == "ALL",])
## Label "ALL" release for any study with just 1 record
benicia_rel[benicia_rel$StudyID %in% names(which(table(benicia_rel$StudyID) ==1)),"Release"] <- "ALL"
wlk_flow <- as.data.frame(cdec_query("WLK", "41", "D", as.Date(min(benicia_rel$RelDT))-7, max(as.Date(max(benicia_rel$RelDT))+14, min(Sys.Date(), as.Date("2021-06-15")))))
wlk_flow$datetime <- as.Date(wlk_flow$datetime)
ma <- function(x, n = 5){stats::filter(x, rep(1 / n, n), sides = 1)}
wlk_flow$ma <- c(ma(wlk_flow$parameter_value, n=7)[-(1:6)], rep(NA,6))
wlk_flow <- wlk_flow[is.na(wlk_flow$ma) == F,]
benicia_rel$datetime <- as.Date(benicia_rel$RelDT)
## do this cuz can't get rid of legend title in ggplotly
benicia_rel$. <- benicia_rel$data_quality

## Now plot

library(ggplot2)

pd <- position_dodge(1)
boolColors <- as.character(c("final"="black", "tentative"="gray"))
boolScale <- scale_colour_manual(name=".", values=boolColors)

ay <- list(
  overlaying = "y",
  nticks = 5,
  color = "blue",
  side = "right",
  title = "7-day moving average of Flow (cfs) at Wilkins Slough",
  automargin = TRUE
)

p <- ggplot(data = benicia_rel, mapping = aes(x=datetime, y=estimate, label = StudyID, text = Release)) +
  xlim(range(wlk_flow$datetime)) +
  geom_errorbar(aes(ymin=lcl, ymax=ucl), colour="black", width=.1, position=pd) +
  geom_point(data = benicia_rel, size=2, position = pd, stroke = 1.5, aes(colour= .)) +
  boolScale +
  labs(x="Release Date", size = 8) +
  labs(y="% Survival to Benicia Bridge", size = 8) +  
  theme(panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "light grey"),
        panel.grid.major.x = element_blank(), 
        panel.grid.minor = element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
        axis.line.y.right = element_line(color = "blue"), 
        axis.title.y.right = element_text(color = "blue"),
        axis.text.y.right = element_text(color = "blue"),
        panel.background = element_rect(fill = "white", colour = "black"),
        legend.position="top",
        panel.border = element_rect(colour = "black", fill=NA))

ggplotly(p, tooltip = c("StudyID", "Release", "estimate"), width = 800, height = 600) %>%
  add_annotations( text="Data status", xref="paper", yref="paper",
                   x=0.25, xanchor="left",
                   y=-0.26, yanchor="bottom",    # Same y as legend below
                   legendtitle=TRUE, showarrow=FALSE ) %>%
  add_lines(x=~as.numeric(wlk_flow$datetime), y=~wlk_flow$ma, line = list(color = "blue"), yaxis="y2", showlegend=FALSE, inherit=FALSE) %>%
  layout(yaxis2 = ay, legend = list(orientation = "h",x = 0.4, y = -0.2), margin=list(
  l = 50,
  r = 100,
  b = 50,
  t = 50
))
       

```


<br>

## 1.2 Through-Delta survival (City of Sacramento to Benicia) for all major Chinook salmon tagging efforts (n > 100).
Hover cursor over points to see release group.
```{r print plot of season total delta survival,fig.height = 6, fig.width = 6, out.extra='style="background-color: #000000; padding:3px"', echo = FALSE, warning=FALSE, message = FALSE, }
library(CDECRetrieve)
library(plotly)

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

benicia <- read.csv("Delta_surv.csv", stringsAsFactors = F)
benicia$RelDT <- as.POSIXct(benicia$RelDT)
benicia <- merge(benicia, tol_released)
## Now remove any release smaller than 100
benicia <- benicia[benicia$total_released >99,]
benicia_rel <- benicia[benicia$Release != "ALL",]
## Now subset to only be WY2019 fish
benicia_rel <- benicia_rel[benicia_rel$RelDT > "2021-01-01" & benicia_rel$RelDT < "2021-12-01",]
## Remove any steelhead releases
benicia_rel <- benicia_rel[grepl("_SH_", benicia_rel$StudyID) == F,]
### Combine sutter bypass releases
#benicia_rel <- benicia_rel[benicia_rel$StudyID != "SB_Spring_2019",]
#benicia_rel <- rbind(benicia_rel, benicia[benicia$StudyID == "SB_Spring_2019" & benicia$Release == "ALL",])
## Label "ALL" release for any study with just 1 record
benicia_rel[benicia_rel$StudyID %in% names(which(table(benicia_rel$StudyID) ==1)),"Release"] <- "ALL"
## download data from a week before first release, to current day (or 6/15, whichever comes first)
wlk_flow <- as.data.frame(cdec_query("RVB", "25", "D", as.Date(min(benicia_rel$RelDT))-7, max(as.Date(max(benicia_rel$RelDT))+14, min(Sys.Date(), as.Date("2021-06-15")))))
wlk_flow$parameter_value <- (wlk_flow$parameter_value - 32) * 5/9
wlk_flow$datetime <- as.Date(wlk_flow$datetime)
ma <- function(x, n = 5){stats::filter(x, rep(1 / n, n), sides = 1)}
wlk_flow$ma <- c(ma(wlk_flow$parameter_value, n=7)[-(1:6)], rep(NA,6))
wlk_flow <- wlk_flow[is.na(wlk_flow$ma) == F,]
benicia_rel$datetime <- as.Date(benicia_rel$RelDT)
## do this cuz can't get rid of legend title in ggplotly
benicia_rel$. <- benicia_rel$data_quality

## Now plot

library(ggplot2)

pd <- position_dodge(1)
boolColors <- as.character(c("final"="black", "tentative"="gray"))
boolScale <- scale_colour_manual(name=".", values=boolColors)

ay <- list(
  overlaying = "y",
  nticks = 5,
  color = "red",
  side = "right",
  title = "7-day moving average of Temperature (C) at Rio Vista",
  automargin = TRUE
)

p <- ggplot(data = benicia_rel, mapping = aes(x=datetime, y=estimate, label = StudyID, text = Release)) +
  xlim(range(wlk_flow$datetime)) +
  geom_errorbar(aes(ymin=lcl, ymax=ucl), colour="black", width=.1, position=pd) +
  geom_point(data = benicia_rel, size=2, position = pd, stroke = 1.5, aes(colour= .)) +
  boolScale +
  labs(x="Release Date", size = 8) +
  labs(y="% through-Delta Survival", size = 8) +  
  theme(panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "light grey"),
        panel.grid.major.x = element_blank(), 
        panel.grid.minor = element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
        axis.line.y.right = element_line(color = "red"), 
        axis.title.y.right = element_text(color = "red"),
        axis.text.y.right = element_text(color = "red"),
        panel.background = element_rect(fill = "white", colour = "black"),
        legend.position="top",
        panel.border = element_rect(colour = "black", fill=NA))

ggplotly(p, tooltip = c("StudyID", "Release", "estimate"), width = 800, height = 600) %>%
  add_annotations( text="Data status", xref="paper", yref="paper",
                   x=0.25, xanchor="left",
                   y=-0.26, yanchor="bottom",    # Same y as legend below
                   legendtitle=TRUE, showarrow=FALSE ) %>%
  add_lines(x=~as.numeric(wlk_flow$datetime), y=~wlk_flow$ma, line = list(color = "red"), yaxis="y2", showlegend=FALSE, inherit=FALSE) %>%
  layout(yaxis2 = ay, legend = list(orientation = "h",x = 0.4, y = -0.2), margin=list(
  l = 50,
  r = 100,
  b = 50,
  t = 50
))
       

```

<br/>
<br/>

## 1.3 Historic survival to Benicia estimates (PROVISIONAL DATA)
Click to expand
```{r Benicia survival pic, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/Survival_to_Benicia.png"))

```

<br/>
<br/>

## 1.4 Historic through-Delta survival estimates (PROVISIONAL DATA)
Click to expand
```{r Delta survival pic, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/Delta_surv1.png"))
```



