---
title: CalFishTrack

output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
  #prettydoc::html_pretty:
  #  theme: cayman
  #  toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(knitr)
library(kableExtra)
library(lubridate)
#library(xtable)
#library(prettydoc)
library(scales)
library(DT)
library(viridis)


```

#  *Central Valley Enhanced*
#  *Acoustic Tagging Project*
```{r logos, echo=FALSE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')
```

<br/>

# *Download Real-time data*

Real-time data can be downloaded via ERDDAP website. Data is *preliminary* and subject to revision:
https://oceanview.pfeg.noaa.gov/erddap/tabledap/FEDcalFishTrack.html

Alternatively, data can be imported directly into R. To do so, please use the following R code [here.](https://github.com/CalFishTrack/real-time/blob/master/data/accessing_ERDDAP_via_R_realtime.R) 

<br/>

# *Download archived and QAQC'd detection data*

Now you can find *QAQCed and Final* real-time and autonomous JSATS detection data for 2013-2019 on ERDDAP at this url:
https://oceanview.pfeg.noaa.gov/erddap/tabledap/FED_JSATS.html

Alternatively, data can be imported directly into R. To do so, please use the following R code [here.](https://github.com/CalFishTrack/real-time/blob/master/data/accessing_ERDDAP_via_R_autonomous.R)

In addition, you can access metadata on all receiver deployments [here.](https://oceanview.pfeg.noaa.gov/erddap/tabledap/FED_JSATS_receivers.csvp?receiver_serial_number%2Creceiver_general_location%2Creceiver_region%2Creceiver_location%2Clatitude%2Clongitude%2Creceiver_river_km%2Creceiver_general_latitude%2Creceiver_general_longitude%2Creceiver_general_river_km%2Creceiver_make%2Creceiver_depth%2Creceiver_start%2Creceiver_end%2Creceiver_last_valid%2Creceiver_data_coverage%2Creceiver_coverage_problem%2Creceiver_agency&orderBy(%22receiver_start%22))

Finally, you can access metadata on all tagged fish [here.](https://oceanview.pfeg.noaa.gov/erddap/tabledap/FED_JSATS_taggedfish.csvp?fish_id%2Cstudy_id%2Cfish_type%2Cfish_origin%2Cfish_release_date%2Ctag_id_hex%2Ctag_id_decimal%2Ctag_weight%2Ctag_model%2Ctag_pulse_rate_interval_nominal%2Ctag_warranty_life%2Cfish_length_type%2Cfish_length%2Cfish_weight%2Crelease_location%2Crelease_latitude%2Crelease_longitude%2Crelease_river_km&distinct()&orderBy(%22fish_id%22))

**This data delivery project is still under development but it is usable now**.

<br/>

If you intend to download data off the ERDDAP website, rather than importing the data directly into R, please follow these instructions:

The dataset title is: JSATS California Fish Tracking. There are many available fields so click on the question mark bubble for an explanation of each field.

A simple data request to get you started would be:

1) Click on the above link

2) Uncheck all variables at the top of webpage.

3) In the "time (Receiver Detection Time, UTC)" field, you need to adjust the start and stop
date. By default it limits the start and stop time to today's date. To expand the 
time range pull the left side of the slider bar all the way to the left. Or you can 
type in the date range if you know it already.

4) Then check only these fields: 
fish_id, 
time, 
study_id, (Go over to the far pulldown box and select only one study_id)
receiver general location, 
receiver_location (Receiver Location (GPS name)), 
receiver_river_km (Receiver River Kilometer, km)

5) In "Server side functions" - in the pull down select "Order by", then in the box to the right select "fish_id", then in next box to right select "time".

6) File type: pick a file type, try *.csv, which can be opened directly with Notepad, Notepad++, or imported into Excel.

This should get you a table of detections (filtered from raw data) that is sorted by FishID and detection time for one Study.


