---
title: |
  | Central Valley Enhanced
  | Acoustic Tagging Project
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
  #prettydoc::html_pretty:
  #  theme: cayman
  #  toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(knitr)
library(kableExtra)
#library(xtable)
#library(prettydoc)


```

```{r logos, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/logos.jpg"), 
               alt = 'logo', 
               style = 'position:absolute; top:10px; right:0px; width:200px;')
```

<br/>
<br/>

```{r spring run pic, echo=FALSE, cache=TRUE}
htmltools::img(src = knitr::image_uri("../data/mill_ck1.jpg"))#, 
               #alt = 'logo', 
               #style = 'position:absolute; top:0px; right:0px; width:100px;')
```
<br/>
<br/>

# *Mill and Deer Creek wild spring-run Chinook salmon*

<br/>

## 2017-2018 Season (PROVISIONAL DATA)
<br/>

## Project Status

PROJECT IS COMPLETE, ALL TAGS ARE NO LONGER ACTIVE

Project has begun, see tagging details below:
```{r print table with fish release details, echo = FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")
latest <- read.csv("latest_download.csv", stringsAsFactors = F)


study_tagcodes <- tagcodes[tagcodes$StudyID == "DeerCk-Wild-2018",]
study_tagcodes$Release_week <- NA

study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-05"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-05") & study_tagcodes$RelDT < as.POSIXct("2018-05-15"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-15") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 3"


release_stats <- aggregate(list(First_release_time = study_tagcodes$RelDT),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = min)
release_stats <- merge(release_stats,
                       aggregate(list(Last_release_time = study_tagcodes$RelDT),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = max),
                       by = c("Release_week"))

                           
release_stats <- merge(release_stats, aggregate(list(Number_fish_released =
                                                       study_tagcodes$TagID_Hex),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {length(unique(x))}),
                       by = c("Release_week"))

release_stats <- merge(release_stats,
                       aggregate(list(Release_location = study_tagcodes$Rel_loc),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Release_rkm = study_tagcodes$Rel_rkm),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = function(x) {head(x,1)}),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_length = study_tagcodes$Length),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = mean),
                       by = c("Release_week"))
release_stats <- merge(release_stats,
                       aggregate(list(Mean_weight = study_tagcodes$Weight),
                           by= list(Release_week = study_tagcodes$Release_week),
                           FUN = mean),
                       by = c("Release_week"))

release_stats[,c("Mean_length", "Mean_weight")] <- round(release_stats[,c("Mean_length", "Mean_weight")],1)

kable(release_stats, format = "html") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
                       

```

<br/>

## Real-time Fish Detections

*Sacramento real-time receivers deployed 2018-02-01, Georgiana_Slough and Sac_BlwGeorgiana receivers deployed 2018-04-16, data current as of `r latest`. All times in Pacific Standard Time.*

<br/>
<center>
#### Detections at Tower Bridge (downtown Sacramento) versus Sacramento River flows at Wilkins Slough
</center>

```{r print figure of fish detections, echo = FALSE, message = FALSE, fig.height = 6, fig.width = 10}

setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(CDECRetrieve)
library(reshape2)

detects_study <- read.csv("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_DeerCk-Wild-2018.csv", stringsAsFactors = F)
detects_study$DateTime_PST <- as.POSIXct(detects_study$DateTime_PST, format = "%Y-%m-%d %H:%M:%S", "Etc/GMT+8")
detects_study <- detects_study[detects_study$general_location == "TowerBridge",]

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %H:%M:%S %p", tz = "Etc/GMT+8")

tagcodes$Release_week <- NA
tagcodes[tagcodes$RelDT < as.POSIXct("2018-05-05"), "Release_week"] <- "Week 1"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-05-05") & tagcodes$RelDT < as.POSIXct("2018-05-15"), "Release_week"] <- "Week 2"
tagcodes[tagcodes$RelDT > as.POSIXct("2018-05-15") & tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 3"

#wlk_flow <- read.csv("wlk.csv")

if (nrow(detects_study) == 0){
  "No detections yet"
  
} else {
  
  detects_study <- merge(detects_study,aggregate(list(first_detect = detects_study$DateTime_PST), by = list(TagCode= detects_study$TagCode), FUN = min))
  
  detects_study$Day <- as.Date(detects_study$first_detect, "Etc/GMT+8")
  
  detects_study <- merge(detects_study, tagcodes[,c("TagID_Hex", "RelDT", "StudyID", "Release_week", "tag_life")], by.x = "TagCode", by.y = "TagID_Hex")
  
  starttime <- as.Date(min(detects_study$RelDT), "Etc/GMT+8")
  endtime <- min(as.Date(c(Sys.time())), max(as.Date(detects_study$RelDT)+detects_study$tag_life))
  

  wlk_flow <- cdec_query("WLK", "20", "H", starttime, endtime+1)

  wlk_flow$datetime <- as.Date(wlk_flow$datetime)
  wlk_flow_day <- aggregate(list(parameter_value = wlk_flow$parameter_value),
                            by = list(Day = wlk_flow$datetime),
                            FUN = mean, na.rm = T)


  daterange <- data.frame(Day = seq.Date(from = starttime, to = endtime, by = "day"))

  rels <- unique(tagcodes[tagcodes$StudyID == unique(detects_study$StudyID), "Release_week"])
  rel_num <- length(rels)
  rels_no_detects <- as.character(rels[!(rels %in% unique(detects_study$Release_week))])

  tagcount <- aggregate(list(unique_tags = detects_study$TagCode), by = list(Day = detects_study$Day, Release_week = detects_study$Release_week ), FUN = function(x){length(unique(x))})
  tagcount1 <- reshape2::dcast(tagcount, Day ~ Release_week)

  daterange1 <- merge(daterange, tagcount1, all.x=T)

  if(length(rels_no_detects)>0){
    for(i in rels_no_detects){
      daterange1 <- cbind(daterange1, x=NA)
      names(daterange1)[names(daterange1) == 'x'] <- paste(i)
    }
  }

  daterange2 <- merge(daterange1, wlk_flow_day, by = "Day", all.x = T)

  rownames(daterange2) <- daterange2$Day
  daterange2$Day <- NULL

  par(mar=c(6, 5, 2, 5) + 0.1)
  barp <- barplot(t(daterange2[,1:ncol(daterange2)-1]), plot = FALSE, beside = T)
  barplot(t(daterange2[,1:ncol(daterange2)-1]), beside = T, col=rainbow(rel_num),
          xlab = "", ylab = "Number of fish arrivals per day",
          ylim = c(0,max(daterange2[,1:ncol(daterange2)-1], na.rm = T)*1.2),
          las = 2, xlim=c(0,max(barp)+1), cex.lab = 1.5, yaxt = "n", xaxt = "n")#,
  #legend.text = colnames(daterange2[,1:ncol(daterange2)-1]),
  #args.legend = list(x ='topright', bty='n', inset=c(-0.2,0)), title = "Release Group")
  legend(x ='topleft', legend = colnames(daterange2[,1:ncol(daterange2)-1]), fill= rainbow(rel_num), horiz = T, title = "Release Week")
  ybreaks <- if(max(daterange2[,1:ncol(daterange2)-1], na.rm = T) < 4) {max(daterange2[,1:ncol(daterange2)-1], na.rm = T)} else {5}
  xbreaks <- if(ncol(barp) > 10) {seq(1, ncol(barp), 2)} else {1:ncol(barp)}
  barpmeans <- colMeans(barp)
  axis(1, at = barpmeans[xbreaks], labels = rownames(daterange2[xbreaks,]), las = 2)
  axis(2, at = pretty(0:max(daterange2[,1:ncol(daterange2)-1], na.rm = T), ybreaks))

  par(new=T)

  plot(x = barpmeans, daterange2$parameter_value, yaxt = "n", xaxt = "n", ylab = "", xlab = "", col = "blue", type = "l", lwd=2, xlim=c(0,max(barp)+1), ylim = c(min(daterange2$parameter_value, na.rm = T), max(daterange2$parameter_value, na.rm=T)*1.1))#, ylab = "Returning adults", xlab= "Outmigration year", yaxt="n", col="red", pch=20)
  axis(side = 4)#, labels = c(2000:2016), at = c(2000:2016))
  mtext("Flow (cfs) at Wilkins Slough", side=4, line=3, cex=1.5, col="blue")
}

```

<br/>
<br/>

</center>
#### Minimum survival to Tower Bridge (using CJS survival model)
</center>

<br/>

```{r print table of survival, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)
library(RMark)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_DeerCk-Wild-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "DeerCk-Wild-2018",]
study_tagcodes$Release_week <- NA
study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-05"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-05") & study_tagcodes$RelDT < as.POSIXct("2018-05-15"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-15") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 3"

study_count <- nrow(study_tagcodes)

if (nrow(test[test$general_location == "TowerBridge",]) == 0){
  "No detections yet"
} else {
  
  test <- merge(test, study_tagcodes[,c("TagID_Hex", "Release_week")], by.x = "TagCode", by.y = "TagID_Hex")
  
  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  
  ## Only do survival to Sac for now
  test <- test[test$rkm > 160,]
  
  ## Create inp for survival estimation
  
  inp <- as.data.frame(reshape2::dcast(test, TagCode ~ rkm, fun.aggregate = length))
  
  ## Sort columns by river km in descending order
  # Count number of genlocs
  gen_loc_sites <- ncol(inp)-1
  
  inp <- inp[,c(1,order(names(inp[,2:(gen_loc_sites+1)]), decreasing = T)+1)]

  inp <- merge(study_tagcodes, inp, by.x = "TagID_Hex", by.y = "TagCode", all.x = T)
  
  inp2 <- inp[,(ncol(inp)-gen_loc_sites+1):ncol(inp)]
  inp2[is.na(inp2)] <- 0
  inp2[inp2 > 0] <- 1
  
  inp <- cbind(inp, inp2)
  groups <- as.character(sort(unique(inp$Release_week)))

  inp[,groups] <- 0
  for (i in groups) {
    inp[as.character(inp$Release_week) == i, i] <- 1
  }
  
  inp$inp_final <- paste("1",apply(inp2, 1, paste, collapse=""), " ",apply(inp[,groups], 1, paste, collapse=" ")," ;",sep = "")
  
  
  write.table(inp$inp_final,"WRinp.inp",row.names = F, col.names = F, quote = F)
  
  WRinp <- convert.inp("WRinp.inp", group.df=data.frame(rel=groups))
  
  WR.process <- process.data(WRinp, model="CJS", begin.time=1, groups = "rel") 
  
  WR.ddl <- make.design.data(WR.process)
  
  WR.mark.all <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time),p=list(formula=~time)), silent = T, output = F)
  
  WR.mark.rel <- mark(WR.process, WR.ddl, model.parameters=list(Phi=list(formula=~time*rel),p=list(formula=~time)), silent = T, output = F)
  
  WR.surv <- round(WR.mark.all$results$real[1,c("estimate", "se", "lcl", "ucl")] * 100,1)
  WR.surv <- rbind(WR.surv, round(WR.mark.rel$results$real[seq(from=1,to=length(groups)*2,by = 2),c("estimate", "se", "lcl", "ucl")] * 100,1))
  WR.surv$Detection_efficiency <- NA
  WR.surv[1,"Detection_efficiency"] <- round(WR.mark.all$results$real[gen_loc_sites+1,"estimate"] * 100,1)
  
  WR.surv <- cbind(c("ALL", groups), WR.surv)
  
  colnames(WR.surv) <- c("Release Week", "Survival (%)", "SE", "95% lower C.I.", "95% upper C.I.", "Detection efficiency (%)")
  
  print(kable(WR.surv, row.names = F, "html") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))

}

cleanup(ask = F)

```    

<br/>

<center>
#### Detections statistics at all realtime receivers
</center>

<br/>

```{r print tables of fish detections, echo = FALSE, message = FALSE, results= "asis", warning=FALSE}
setwd(paste(file.path(Sys.getenv("USERPROFILE"),"Desktop",fsep="\\"), "\\Real-time data massaging\\products", sep = ""))

library(data.table)

test <- fread("C:/Users/field/Desktop/Real-time data massaging/products/Study_detection_files/detects_DeerCk-Wild-2018.csv", stringsAsFactors = FALSE)
gen_locs <- read.csv("realtime_locs.csv", stringsAsFactors = F)

tagcodes <- read.csv("qry_HexCodes.txt", stringsAsFactors = F)
tagcodes$RelDT <- as.POSIXct(tagcodes$RelDT, format = "%m/%d/%Y %I:%M:%S %p", tz = "Etc/GMT+8")

study_tagcodes <- tagcodes[tagcodes$StudyID == "DeerCk-Wild-2018",]
study_tagcodes$Release_week <- NA
study_tagcodes[study_tagcodes$RelDT < as.POSIXct("2018-05-05"), "Release_week"] <- "Week 1"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-05") & study_tagcodes$RelDT < as.POSIXct("2018-05-15"), "Release_week"] <- "Week 2"
study_tagcodes[study_tagcodes$RelDT > as.POSIXct("2018-05-15") & study_tagcodes$RelDT < as.POSIXct("2018-05-20"), "Release_week"] <- "Week 3"

study_count <- nrow(study_tagcodes)

if (nrow(test) == 0){
  "No detections yet"
} else {
  
  test <- merge(test, study_tagcodes[,c("TagID_Hex", "Release_week")], by.x = "TagCode", by.y = "TagID_Hex")

  test$DateTime_PST <- as.POSIXct(test$DateTime_PST, format = "%Y-%m-%d %H:%M:%S")
  tag_stats <- aggregate(list(First_arrival = test$DateTime_PST), 
                         by= list(general_location = test$general_location),
                         FUN = min)
  tag_stats <- merge(tag_stats, 
                     aggregate(list(Mean_arrival = test$DateTime_PST), 
                         by= list(general_location = test$general_location),
                         FUN = mean), 
                     by = c("general_location"))
  tag_stats <- merge(tag_stats, 
                     aggregate(list(Fish_count = test$TagCode), 
                         by= list(general_location = test$general_location), 
                         FUN = function(x) {length(unique(x))}), 
                     by = c("general_location"))
  tag_stats$Percent_arrived <- round(tag_stats$Fish_count/study_count * 100,2)
      
  tag_stats <- merge(tag_stats, unique(gen_locs[,c("general_location", "rkm")]))
  
  tag_stats <- tag_stats[order(tag_stats$rkm, decreasing = T),]
  
  print(kable(tag_stats, row.names = F, 
              caption = "Detections for all release weeks combined",
              "html") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
  
  for (j in sort(unique(study_tagcodes$Release_week))) {
    
    if(nrow(test[test$Release_week == j,]) > 0 ) {
    
      temp <- test[test$Release_week == j,]
  
      rel_count <- nrow(study_tagcodes[study_tagcodes$Release_week == j,])
  
      tag_stats1 <- aggregate(list(First_arrival = temp$DateTime_PST), 
                             by= list(general_location = temp$general_location), 
                             FUN = min)
      tag_stats1 <- merge(tag_stats1, 
                         aggregate(list(Mean_arrival = temp$DateTime_PST), 
                             by= list(general_location = temp$general_location), 
                             FUN = mean), 
                         by = c("general_location"))
      tag_stats1 <- merge(tag_stats1, 
                         aggregate(list(Fish_count = temp$TagCode), 
                                   by= list(general_location = temp$general_location), 
                                   FUN = function(x) {length(unique(x))}), 
                         by = c("general_location"))
      
      tag_stats1$Percent_arrived <- round(tag_stats1$Fish_count/rel_count * 100,2)
    
      tag_stats1 <- merge(tag_stats1, unique(gen_locs[,c("general_location", "rkm")]))
    
      tag_stats1 <- tag_stats1[order(tag_stats1$rkm, decreasing = T),]
    
      final_stats <- kable(tag_stats1, row.names = F, 
            caption = paste("Detections for",j,"release groups", sep = " "),
            "html")
      print(kable_styling(final_stats, bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left"))
      
    } else {
      cat("\n\n\\pagebreak\n")
      print(paste("No detections for",j,"release group yet", sep=" "), quote = F)
      cat("\n\n\\pagebreak\n")
    }
  }
}

```
